\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
proof poging

%------------------------------------------------
\section{Description of Algorithms}
For hard instances of the graph isomorphism problem, the coarsest stable coloring of a graph still has a lot of colors which are not unique. Two structures for which this is the case are twins and false twins, they are defined in definition \ref{deftwins} and \ref{deffalsetwins}.
\begin{definition}
Let $G = (V,E)$ be a graph. The \emph{neighbourhood} $N(v)$ of $v \in V$ is:
$N(v) = \left\{{u \in V : \{u,v\} \in E}\right\}$
\end{definition}
\begin{definition}\label{deftwins}
Let $G = (V,E)$ be a graph.
Two vertices $u, v \in V$ are \emph{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash {v} = N(v)\textbackslash {u}$.
\end{definition}
\begin{definition}\label{deffalsetwins}
Let $G = (V,E)$ be a graph.
Two vertices $u, v \in V(G)$ are \emph{false twins} if $N(u) = N(v).$
\end{definition}

To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms which replaces twins and false twins by single precolored vertices such that:
\begin{compactenum}
\item Twins have the same color $\iff$ Twins have the same size (number of vertices).
\item False twins have the same color $\iff$ False twins have the same size (number of vertices).
\item A twin and a false twin can't have the same color.
\end{compactenum}

@@

\subsubsection{Replacing the twins}
The algorithm \emph{preprocessing} can be found in appendix \ref{preprocessing}. In line 2 the twins and falsetwins are defined and if there are none the program will terminate. If there are any twins all edges with a head or tail in one of these twins will be deleted. The complexity of this is $O(m +$ number of vertices (\emph{twins}+\emph{falsetwins}))$ < O (nm)$. Then in line 13-19 all vertices which are in twins or falsetwins will be removed. The complexity of this is $O(n^2)$. In line 20-28 a new colored vertex will be added for each (false) twin $(O(n)$ and finnaly the edges from these vertices will be added ($O(n^2 (n+m)$). The worst case complexity of this algorithm is ($O(n^2 (n+m)$), however in average there are much less (false) twins than vertices (there are at most $n/2$). These twins also have much less than $n$ neighbours.

%------------------------------------------------
\section{Proof of Correctness}
NOG NIET AF!
\begin{definition}
A \emph{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
\end{definition}
\begin{definition}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs. A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if \begin{compactenum}[\upshape(a)]
\item $f$ is a bijection, 
\item for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and 
\item $color(v)$ = $color (f(v)$. When such a function exist, $G_1$ and $G_2$ are called \emph{isomorphic graphs}. 
\end{compactenum}
\end{definition}
\begin{theorem}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs where each vertex has the same color and let $H_1 = (V_1, E_1)$ and $H_2 = (V_2, E_2)$ be resp. the same graphs as $G_1$ and $G_2$ where each (false) twin is replaced by a colored vertex such that: \begin{compactenum}[\upshape(a)]
\item Twins (False twins) have the same color $\iff$ Twins (False twins) have the same size (number of vertices).
\item A twin and a false twin can't have the same color.
\end{compactenum}
Graph $G_1$ and $G_2$ are isomorphic $\iff$ Graph $H_1$ and $H_2$ are isomorphic.
\end{theorem}
\begin{proof}
Todo
\end{proof}

@@

\section{Table with computation times}
\begin{table}[h]
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
products72 & 7.5950 sec & 7.5198 sec & 0.0275 sec\\
torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}
\end{appendices}

>>>>

%------------------------------------------------
\section{Description of Algorithms}
For hard instances of the graph isomorphism problem, the coarsest stable coloring of a graph still has a lot of colors which are not unique. Two structures for which this is the case are twins and false twins, they are defined in definition \ref{deftwins} and \ref{deffalsetwins}.
\begin{definition}
Let $G = (V,E)$ be a graph. The \emph{neighbourhood} $N(v)$ of $v \in V$ is:
$N(v) = \left\{{u \in V : \{u,v\} \in E}\right\}$
\end{definition}
\begin{definition}\label{deftwins}
Let $G = (V,E)$ be a graph.
Two vertices $u, v \in V$ are \emph{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash \{v\} = N(v)\textbackslash \{u\}$.
\end{definition}
\begin{definition}\label{deffalsetwins}
Let $G = (V,E)$ be a graph.
Two vertices $u, v \in V(G)$ are \emph{false twins} if $N(u) = N(v).$
\end{definition}

To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms which replaces twins and false twins by single precolored vertices such that:
\begin{compactenum}
\item Vertices in the new graph have the same color $\iff$ The corresponding twinsets or false twinsets in the old graph have the same size (number of vertices).
\item Two vertices in the new graph can't have the same color if one of them corresponds to a twinset and the other one two a false twinset in the old graph.
\end{compactenum}

@@

\subsubsection{Replacing the twins}
The algorithm \emph{preprocessing} can be found in appendix \ref{preprocessing}. In line 2 the twins and falsetwins are defined and if there are none the program will terminate. If there are any twins all edges with a head or tail in one of these twins will be deleted. The complexity of this is $O(m +$ number of vertices in (\emph{twins}+\emph{falsetwins}))$ < O (nm)$. Then in line 13-19 all vertices which are in twins or falsetwins will be removed. The complexity of this is $O(n^2)$. In line 20-28 a new colored vertex will be added for each (false) twin $(O(n)$ and finnaly the edges from these vertices will be added ($O(n^2 (n+m)$). The worst case complexity of this algorithm is ($O(n^2 (n+m)$), however in average there are much less (false) twins than vertices (there are at most $n/2$). These twins also have much less than $n$ neighbours.

%------------------------------------------------
\section{Proof of Correctness}
NOG NIET AF!
\begin{definition}
A \emph{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
\end{definition}
\begin{definition}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs. A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if \begin{compactenum}[\upshape(a)]
\item $f$ is a bijection, 
\item for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and 
\item $color(v)$ = $color (f(v)$. When such a function exist, $G_1$ and $G_2$ are called \emph{isomorphic graphs}. 
\end{compactenum}
\end{definition}
\begin{theorem}
Let $G_1 = (V_{G1}, E_{G1})$ and $G_2 = (V_{G2}, E_{G2})$ be two undirected colored graphs where each vertex has color 0 and let $H_1 = (V_{H1}, E_{H1})$ and $H_2 = (V_{H2}, E_{H2})$ be resp. the same graphs as $G_1$ and $G_2$ where each (false) twin is replaced by a colored vertex such that: \begin{compactenum}[\upshape(a)]
\item Vertices in $H_1$ ($H_2$) have the same color $\iff$ The corresponding twinsets or false twinsets in $G_1$ ($G_2$) have the same size (number of vertices).
\item Two vertices in $H_1$ ($H_2$) can't have the same color if one of them corresponds to a twinset in $G_1$ ($G_2$) and the other one corresponds to a false twinset in $G_1$ ($G_2$). They also can't have color 0.
\end{compactenum}
Graph $G_1$ and $G_2$ are isomorphic $\iff$ Graph $H_1$ and $H_2$ are isomorphic.
\end{theorem}
\begin{proof}
$\Leftarrow$:  $\exists$ graph isomorphism $h: H_1 \to H_2$. We want to proof that $g: G_1 \to G_2$ is a graph isomorphism. If $v \in V_{H1}$ has color 0 we define $g(v) = h(v)$.  If $v \in V_{H1}$ has color $\neq$ 0, $\exists$ $ w \in V_{H2}$ such that color($v$) = color($w$) (since $H_1$ and $H_2$ are isomorphs). $v$ and $w$ either have resp. corresponding false twinsets \emph{ftw} $\subseteq V_{G1}$ and \emph{ftw2} $\subseteq V_{G2}$ or they have resp. corresponding twinsets \emph{tw} $\subseteq V_{G1}$ and \emph{tw2} $\subseteq V_{G2}$. In the first case map each $x \in$ \emph{ftw} to a different $y \in$ \emph{ftw2}. Since they are false twins it doesn't matter which $x$ is mapped to which $y$.

Similar for twins

\end{proof}

@@

\section{Table with computation times}
\begin{table}[h]
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
products72 & 7.5950 sec & 7.5198 sec & 0.0275 sec\\
torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}

\section{Complexity}
\begin{table}[h]
\begin{tabular}{c|c}
n & time \\
\hline
34 & 0.0017\\
66 & 0.0032\\
130 & 0.0071\\
258 & 0.161\\
514 & 0.0344\\
1026 & 0.0805\\
2050 & 0.2019\\
4098 & 0.5874\\
8194 & 2.7102

\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}
\end{appendices}
